---
title: "LKT Examples"
output: md_document
---

# LKT [![](https://cranlogs.r-pkg.org/badges/LKT)](https://cran.r-project.org/package=LKT)

# Examples are here, but also please see the manual and vignette.

# Load data
```{r}
library(LKT)
# data.table is the base data type
library(data.table)
datafile<-"C:\\Users\\ppavl\\OneDrive - The University of Memphis\\IES Data\\ds1465_tx_All_Data_64_2016_0720_222352.txt" # CHANGE THIS VALUE TO THE DataShop export file IN YOUR R WORKING DIRECTORY
val<-read.table(colClasses = c("Anon.Student.Id"="character"),datafile,sep="\t", header=TRUE,quote="\"")
# val<-val[1:2000,]
# make it a datatable
val= setDT(val)

#make sure it is ordered in the way the code expects
val<-val[order(val$Anon.Student.Id, val$Time),]

#create a binanry response column to predict and extract only data with a valid value
val$CF..ansbin.<-ifelse(tolower(val$Outcome)=="correct",1,ifelse(tolower(val$Outcome)=="incorrect",0,-1))
val<-val[val$CF..ansbin==0 | val$CF..ansbin.==1,]

# get the times of each trial in seconds from 1970
val$CF..Time.<-as.numeric(as.POSIXct(as.character(val$Time),format="%Y-%m-%d %H:%M:%S"))

# create durations
val$Duration..sec.<-(val$CF..End.Latency.+val$CF..Review.Latency.+500)/1000

# this function needs times and durations but you don't need it if you don't want to model time effects
val <- computeSpacingPredictors(val, "KC..Default.") #allows recency, spacing, forgetting features to run
```

# AFM fixed effect version
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id","KC..Default.","KC..Default."),
  features = c("intercept", "intercept", "lineafm"))
```

# PFA fixed effect version
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "linesuc","linefail"))

# have to have prior predictions in data to do the next model in and adaptive system
#   this needs to be added to the data as it is collected
val$pred<-modelob$prediction
```

PFA random effect version too slow for seminar and mostly just to allow comparison models (impractical)
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept@", "intercept", "linesuc","linefail"))

#PFA using difficulty sensitive predictors (composite model requiring pred from prior model)
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "diffcorComp","linefail"))
```

# RPFA
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "propdec2","linefail"),
  fixedpars=c(.9))
```

# Recency tracing with logitdec
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "logitdec","recency"),
  fixedpars=c(.9,.5))
```

# Recency tracing with RPFA propdec2 feature
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "propdec2","recency"),
  fixedpars=c(NA,NA))
```

# PPE
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "ppe","logitdec"),
  fixedpars=c(0.3491901,0.2045801,1e-05,0.9734477,0.4443027))
```

# base4
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
  features = c("intercept", "intercept", "base4","logitdec"),
  fixedpars=c(0.1890747,0.6309054,0.05471752,.5,0.2160748))
```

#Using other features
#See LKT paper
#See computefeatures function in the main R code for package
#https://github.com/Optimal-Learning-Lab/LKT/blob/master/R/LKTfunctions.R

# Covariates
```{r}
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("Anon.Student.Id","KC..Default.","KC..Default."),
  features = c("logitdec", "logitdec", "lineafm"),fixedpars=c(.9,.8),
  covariates = c(NA,NA,"Level..Unitname."))
```

# Crossvalidation
```{r}
# make folds
unq = sample(unique(val$Anon.Student.Id))
sfold = rep(1:5,length.out=length(unq))
val$fold = rep(0,length(val[,1]))
for(i in 1:5){val$fold[which(val$Anon.Student.Id %in% unq[which(sfold==i)])]=i}

#simple AFM minus student intercept
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("KC..Default.","KC..Default."),
  features = c("intercept", "lineafm"),
  cv = TRUE)
mean(modelob$cv_res$mcfad)

#complex AFM minus student intercept
modelob <- LKT(
  data = val, interc=TRUE,
  components = c("KC..Default.","KC..Default."),
  features = c("intercept$", "lineafm$"),
  cv = TRUE)
mean(modelob$cv_res$mcfad)
```
