---
title: "Examples"
author: "Philip I. Pavlik Jr."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Load data
=========

Get the data free:

<a href="https://datashop.memphis.edu/DatasetInfo?datasetId=1465" class="uri">https://datashop.memphis.edu/DatasetInfo?datasetId=1465</a>

```{r, echo=TRUE}
    library(LKT)


    # data.table is the base data type
    library(data.table)
    
    setwd("C:/Users/ppavl/OneDrive - The University of Memphis/IES Data")
    datafile<-"ds1465_tx_All_Data_64_2016_0720_222352.txt" 
    val<-read.table(colClasses = c("Anon.Student.Id"="character"),datafile,sep="\t", header=TRUE,quote="\"")

    # make it a datatable
    val= setDT(val)

    #make unstratified folds for crossvaldiations
    val$fold<-sample(1:5,length(val$Anon.Student.Id),replace=T)

    # get the times of each trial in seconds from 1970
    val$CF..Time.<-as.numeric(as.POSIXct(as.character(val$Time),format="%Y-%m-%d %H:%M:%S"))
    
    #make sure it is ordered in the way the code expects
    val<-val[order(val$Anon.Student.Id, val$CF..Time.),]

    #create a binary response column to predict and extract only data with a valid value
    val$CF..ansbin.<-ifelse(tolower(val$Outcome)=="correct",1,ifelse(tolower(val$Outcome)=="incorrect",0,-1))
    val<-val[val$CF..ansbin==0 | val$CF..ansbin.==1,]

   

    # create durations
    val$Duration..sec.<-(val$CF..End.Latency.+val$CF..Review.Latency.+500)/1000

    # this function needs times and durations but you don't need it if you don't want to model time effects
    val <- computeSpacingPredictors(val, "KC..Default.") #allows recency, spacing, forgetting features to run
```


# Additive Factors Model (AFM) fixed effect version

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id","KC..Default.","KC..Default."),
      features = c("intercept", "intercept", "lineafm$"))
```

# Performance Factors Analysis (PFA) fixed effect version

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "linesuc$","linefail$"))
    # have to have prior predictions in data to do the next model in and adaptive system
    #   this needs to be added to the data wth a first moodel like this
    val$pred<-modelob$prediction
```

PFA random effect version too slow for seminar and mostly just to allow
comparison models (impractical) modelob &lt;- LKT( data = val,
interc=TRUE, components = c(“Anon.Student.Id”, “KC..Default.”,
“KC..Default.”, “KC..Default.”), features = c(“intercept@”, “intercept”,
“linesuc”,“linefail”))

# PFA using difficulty sensitive predictors (composite model requiring pred from prior model)

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "linesuc$","linefail$"))
    # have to have prior predictions in data to do the next model in and adaptive system
    #   this needs to be added to the data wth a first moodel like this
    val$pred<-modelob$prediction
    
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "diffcorComp","linefail"))
```

# Recent Performance Factors Analysis (RPFA)

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "propdec2","linefail"),
      fixedpars=c(.9))
```

# Recency tracing with logitdec

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "logitdec","recency"),
      fixedpars=c(.9,.5))
```

# Recency tracing with logitdec and transfer from cluster

```{r, echo=TRUE}

modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default.","KC..Cluster."),
      features = c("intercept", "intercept", "logitdec","recency","logitdec"),
      fixedpars=c(.9,.5,.5))
```

# Recency tracing with RPFA propdec2 feature

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "propdec2","recency"),
      fixedpars=c(NA,NA))
```

# Performance Prediction Equation (PPE)

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "ppe","logitdec"),
      fixedpars=c(0.3491901,0.2045801,1e-05,0.9734477,0.4443027))
```

# base4

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default.", "KC..Default."),
      features = c("intercept", "intercept", "base4","logitdec"),
      fixedpars=c(0.1890747,0.6309054,0.05471752,.5,0.2160748))
```

Using other features #See LKT paper #See computefeatures function in
the main R code for package
<a href="https://github.com/Optimal-Learning-Lab/LKT/blob/master/R/LKTfunctions.R" class="uri">https://github.com/Optimal-Learning-Lab/LKT/blob/master/R/LKTfunctions.R</a>


# Covariates

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id","KC..Default.","KC..Default."),
      features = c("logitdec", "logitdec", "lineafm"),fixedpars=c(.9,.8),
      covariates = c(NA,NA,"Level..Unitname."))
```

# Individualized Additive Factors Model (iAFM) fixed effect version

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("Anon.Student.Id","KC..Default.","KC..Default.","KC..Default."),
      features = c("intercept", "intercept", "lineafm$","lineafm"),
      covariates = c(NA,NA,NA,"Anon.Student.Id"))
```

# Crossvalidation

```{r, echo=TRUE}
# make student stratified folds (for crossvalidation for unseen population)
    unq = sample(unique(val$Anon.Student.Id))
    sfold = rep(1:5,length.out=length(unq))
    val$fold = rep(0,length(val[,1]))
    for(i in 1:5){val$fold[which(val$Anon.Student.Id %in% unq[which(sfold==i)])]=i}

    #simple AFM minus student intercept
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("KC..Default.","KC..Default."),
      features = c("intercept", "lineafm"),
      cv = TRUE)
    mean(modelob$cv_res$mcfad)

    #complex AFM minus student intercept
    modelob <- LKT(
      data = val, interc=TRUE,
      components = c("KC..Default.","KC..Default."),
      features = c("intercept$", "lineafm$"),
      cv = TRUE)
    mean(modelob$cv_res$mcfad)
```

# Connectors

```{r, echo=TRUE}
    modelob <- LKT(
      data = val, interc=TRUE,
      connectors = c("+","+","*"),
      components = c("Anon.Student.Id", "KC..Default.", "KC..Default."),
      features = c("logitdec", "logitdec$", "lineafm$"),
      fixedpars = c(.9, .85) )
```

# AutoKC

```{r, echo=TRUE}
      modelob <- LKT(data = val, interc=TRUE,
                     components = c("Anon.Student.Id","KC..Default.", "KC..Default.", "KC..Default."),
                     features = c("intercept","intercept",  "linesuc$","linefail$"),cv=TRUE)
      mean(modelob$cv_res$mcfad)
    cat("\n\n")
      
      modelob <- LKT(autoKC=c(F,F,F,F,T,T),autocent=2, data = val, interc=TRUE,
                     components = c("Anon.Student.Id","KC..Default.", "KC..Default.", "KC..Default." ,"KC..Default." ,"KC..Default."),
                     features = c("intercept","intercept",  "linesuc$", "linefail$", "linesuc$", "linefail$")
                     ,cv=TRUE)
      mean(modelob$cv_res$mcfad)
      val
       cat("\n\n")
       
       modelob <- LKT(autoKC=c(F,F,F,T,F,T),autocent=4, data = val, interc=TRUE,connectors = c("+","+","+","*","+","*"),
                     components = c("Anon.Student.Id","KC..Default.", "KC..Default.", "KC..Default." ,"KC..Default." ,"KC..Default."),
                     features = c("intercept","intercept",  "linesuc$", "linesuc$", "linefail$", "linefail$")
                     ,cv=TRUE)
      mean(modelob$cv_res$mcfad)
       cat("\n\n")
       
       
       
          
       modelob <- LKT(autoKC=c(F,F,F,T,F,T),autocent=4, data = val, interc=TRUE,connectors = c("+","+","+","*","+","*"),
                     components = c("Anon.Student.Id","KC..Default.", "KC..Default.", "KC..Default." ,"KC..Default." ,"KC..Default."),
                     features = c("intercept","intercept",  "linesuc", "linesuc$", "linefail", "linefail$")
                     ,cv=TRUE)
      mean(modelob$cv_res$mcfad)
       cat("\n\n")
       
          
       modelob <- LKT(autoKC=c(F,F,F,T,F,T),autocent=4, data = val, interc=TRUE,connectors = c("+","+","+","*","+","*"),
                     components = c("Anon.Student.Id","KC..Default.", "KC..Default.", "KC..Default." ,"KC..Default." ,"KC..Default."),
                     features = c("intercept","intercept",  "linesuc$", "linesuc", "linefail$", "linefail")
                     ,cv=TRUE)
      mean(modelob$cv_res$mcfad)
       cat("\n\n")
       
       
       
       modelob <- LKT(autoKC=c(F,F,F,F,T,T),autocent=8, data = val, interc=TRUE,
                     components = c("Anon.Student.Id","KC..Default.", "KC..Default.", "KC..Default." ,"KC..Default." ,"KC..Default."),
                     features = c("intercept","intercept",  "linesuc$", "linefail$", "linesuc$", "linefail$")
                     ,cv=TRUE)
      mean(modelob$cv_res$mcfad)
       cat("\n\n")
```

